---
title: "FSIM Plots"
author: "Colin Bailey"
date: "2024-10-22"
output: html_document
---

The plots you care about are FUll_Sum Plots Finall Success - just need to work backwords to create the data that go into that section


# Load
```{r}
rm(list=ls())

round2 = function(x, digits) {
  posneg = sign(x)
  z = abs(x)*10^digits
  z = z + 0.5 + sqrt(.Machine$double.eps)
  z = trunc(z)
  z = z/10^digits
  z*posneg
}
library(openxlsx)
library(scales)
library(RColorBrewer); library(tidyverse) 
library(ggplot2); library(dplyr); library(tidyr)
library(cowplot)
theme_set(theme_cowplot())

CUs <- c("Middle_Fraser","Fraser_Canyon","Lower_Thompson","North_Thompson","South_Thompson")
CUnm <- c("Middle Fraser","Fraser Canyon","Lower Thompson","North Thompson","South Thompson")
xcol=c('#8c510a','#d8b365','#c7eae5','#5ab4ac','#01665e') # colours of curves et al.
Ccols <- c("0-0.10" = '#d01c8b', "0.11-0.33" = '#f1b6da', 
           "0.34-0.65" = '#f7f7f7', 
           "0.66-0.89" = '#b8e186', "0.90-1" = '#4dac26')
Ccols2 <- c("< -49" = '#d01c8b', "-49:-30" = '#f1b6da', 
           "-29:29" = '#f7f7f7', 
           "30:49" = '#b8e186', "> 49" = '#4dac26')
```

# Read in Data
```{r}
obsr=read.csv(file="Data_in\\IFCoho_SRbyCU.csv",header=T)
```

# Full_Output Summaries
```{r}
full_out <- read.table(paste("Data_out/Fsim_All_Models_Full_Output", ".out", sep = ""), header = T)

full_out$traj_prop <- ifelse(full_out$traj_percent > 0 , 1, 0)

fuller <- unique(full_out$baseER)
fullSTAS <- unique(full_out$baseSTAS)
models <- unique(full_out$Model)

STASstable <- c(obsr$STAS_Age_3[obsr$CU_ID == 5 & obsr$BroodYear > 2009], obsr$STAS_Age_4[nrow(obsr)])

aveER = exp(mean(log(c(0.205,	0.358,	0.24,	0.092,	0.097,	0.153,	0.217,	0.137,	0.095))))
aveSTAS = exp(mean(log(STASstable))) #geometric mean of STAS
minSTAS = min(fullSTAS)
maxER = 0.5
sdER = 0.057
STASsdlo = exp(mean(log(STASstable))-sd(log(STASstable)))
STASsdhi = exp(mean(log(STASstable))+sd(log(STASstable)))

```

# Bootstrapped Confidence Intervals
Never to be run again! Lol. It just took 3 hours... So just need to read in the new file!
```{r}
write(file = "Data_out/Fsim_BootStrapped_Data.out", 
      "baseER baseSTAS prop.fin traj.prop", ncolumns = 1, append = F)

for(er in fuller){
  full_erA <- full_out[full_out$baseER == er, ]

  for(STAS in fullSTAS){
    full_datA <- full_erA[full_erA$baseSTAS == STAS, ]
  
    for(n in 1:500){
#    for(n in 1:100){
    
      sam <- sample(1500, size = 1500, replace = TRUE)
#      sam <- sample(300, size = 300, replace = TRUE)
      
#            bootdat <- full_datA[sam, ]
            bootdat <- full_datA[sam, ] %>% na.omit()

      
      boot_row = data.frame(
        baseER = er,
        baseSTAS = STAS,
        prop.fin = round2(mean(bootdat$end.suc), 2),
        traj.prop = round(mean(bootdat$traj_prop), 2))
      
      write.table(file="Data_out/Fsim_BootStrapped_Data.out",
          boot_row, append=T, row.names = F, col.names = F)
    }
  }
}
```

Read in BootStrapped values
```{r}
bootCI <- read.table("Data_out/Fsim_BootStrapped_Data.out", header = T)
```

# Summary Table
```{r}

write(file = "Data_out/Fsim_Summary_Data.out", 
      "baseER baseSTAS endsuc endsuc10 endsuc90 freqsuc freq10 freq50 freq90 trajmean traj10 traj50 traj90 trajprop trajpop10 trajpop90", ncolumns = 1, append = F)

for(er in fuller){
  full_erA <- full_out[full_out$baseER == er, ]
  boot_erA <- bootCI[bootCI$baseER == er, ]
  for(STAS in fullSTAS){
    full_datA <- full_erA[full_erA$baseSTAS == STAS, ]
    boot_datA <- boot_erA[boot_erA$baseSTAS == STAS, ]
    
    full_sum <- data.frame(ER = er,
                           STAS = STAS,
                           prop.fin = round(mean(full_datA$end.suc), 2),
                           prop.fin.10 = round(quantile(boot_datA$prop.fin, prob = 0.1), 2),
                           prop.fin.90 = round(quantile(boot_datA$prop.fin, prob = 0.9), 2),
                           prop.all = round(mean(full_datA$freq.suc), 2),
                           all.10 = round(quantile(full_datA$freq.suc, prob = 0.1), 2),
                           all.50 = round(quantile(full_datA$freq.suc, prob = 0.5), 2),
                           all.90 = round(quantile(full_datA$freq.suc, prob = 0.9), 2),
                           traj.mean = round(mean(full_datA$traj_percent), 0),
                           traj.10 = round(quantile(full_datA$traj_percent, prob = 0.1), 0),
                           traj.50 = round(quantile(full_datA$traj_percent, prob = 0.5), 0),
                           traj.90 = round(quantile(full_datA$traj_percent, prob = 0.9), 0),
                           traj.prop = round(mean(full_datA$traj_prop), 2),
                           traj.prop.10 = round(quantile(boot_datA$traj.prop, prob = 0.1), 2),
                           traj.prop.90 = round(quantile(boot_datA$traj.prop, prob = 0.9), 2))
    
#    write.table(file="./Fsim_Full_Output/Fsim_Summary_Data_2.out",
    write.table(file="Data_out/Fsim_Summary_Data.out",
          full_sum, append=T, row.names = F, col.names = F)
  }
}
```


# Full Summary
```{r}
full_summary <- read.table(file="Data_out/Fsim_Summary_Data.out", header = T)
#full_summary <- read.table(file="./Fsim_Full_Output/Fsim_Summary_Data_2.out", header = T)

full_summary$fros.median <- with(full_summary, paste(freq50, " (", freq10, ", ", freq90, ")", sep = ""))
full_summary$traj.median <- with(full_summary, paste(traj50, " (", traj10, ", ", traj90, ")", sep = ""))

full_summary$fros.mean <- with(full_summary, paste(freqsuc, " (", freq10, ", ", freq90, ")", sep = ""))
full_summary$traj.mean <- with(full_summary, paste(trajmean, " (", traj10, ", ", traj90, ")", sep = ""))

full_summary <- full_summary[order(full_summary$baseER, full_summary$baseSTAS), ]

full_summary0 <- full_summary

reduced_summary <- full_summary %>% 
  filter(baseER %in% c(0, 0.03, 0.068, 0.125, 0.183, 0.20, 0.25, 0.30, 0.35, 0.4, 0.45, 0.5),
         baseSTAS %in% c(0.003, 0.007, 0.010, 0.016, 0.021, 0.04))

write.csv(reduced_summary, "Data_out/Fsim_Reduced_Summary.csv", row.names = F)

full_summary <- full_summary %>% filter(baseER < 0.51, baseSTAS < 0.041,
                        baseER != 0.068, baseER != 0.125, baseER != 0.183,
                        baseSTAS != 0.0045, baseSTAS != 0.0141, baseSTAS != 0.0237)

fros.median <- data.frame(Exploitation.Rate = unique(full_summary$baseER),  
                    matrix(full_summary$fros.median, 
                           nrow = length(unique(full_summary$baseER)), 
                           ncol = length(unique(full_summary$baseSTAS)), 
                           byrow = TRUE))

colnames(fros.median)[2:ncol(fros.median)] <- unique(full_summary$baseSTAS)

traj.median <- data.frame(Exploitation.Rate = unique(full_summary$baseER),  
                    matrix(full_summary$traj.median, 
                           nrow = length(unique(full_summary$baseER)), 
                           ncol = length(unique(full_summary$baseSTAS)), 
                           byrow = TRUE))

colnames(traj.median)[2:ncol(traj.median)] <- unique(full_summary$baseSTAS)

traj.mean <- data.frame(Exploitation.Rate = unique(full_summary$baseER),  
                    matrix(full_summary$traj.mean, 
                           nrow = length(unique(full_summary$baseER)), 
                           ncol = length(unique(full_summary$baseSTAS)), 
                           byrow = TRUE))

colnames(traj.mean)[2:ncol(traj.mean)] <- unique(full_summary$baseSTAS)

fin.prop <- data.frame(Exploitation.Rate = unique(full_summary$baseER),  
                    matrix(full_summary$endsuc, 
                           nrow = length(unique(full_summary$baseER)), 
                           ncol = length(unique(full_summary$baseSTAS)), 
                           byrow = TRUE))

colnames(fin.prop)[2:ncol(fin.prop)] <- unique(full_summary$baseSTAS)

traj.prop <- data.frame(Exploitation.Rate = unique(full_summary$baseER),  
                    matrix(full_summary$trajprop, 
                           nrow = length(unique(full_summary$baseER)), 
                           ncol = length(unique(full_summary$baseSTAS)), 
                           byrow = TRUE))

colnames(traj.prop)[2:ncol(traj.prop)] <- unique(full_summary$baseSTAS)

```

### Reduced
```{r}
fros.medianR <- data.frame(Exploitation.Rate = unique(reduced_summary$baseER),  
                    matrix(reduced_summary$fros.median, 
                           nrow = length(unique(reduced_summary$baseER)), 
                           ncol = length(unique(reduced_summary$baseSTAS)), 
                           byrow = TRUE))

colnames(fros.medianR)[2:ncol(fros.medianR)] <- unique(reduced_summary$baseSTAS)

traj.medianR <- data.frame(Exploitation.Rate = unique(reduced_summary$baseER),  
                    matrix(reduced_summary$traj.median, 
                           nrow = length(unique(reduced_summary$baseER)), 
                           ncol = length(unique(reduced_summary$baseSTAS)), 
                           byrow = TRUE))

colnames(traj.medianR)[2:ncol(traj.medianR)] <- unique(reduced_summary$baseSTAS)

traj.meanR <- data.frame(Exploitation.Rate = unique(reduced_summary$baseER),  
                    matrix(reduced_summary$traj.mean, 
                           nrow = length(unique(reduced_summary$baseER)), 
                           ncol = length(unique(reduced_summary$baseSTAS)), 
                           byrow = TRUE))

colnames(traj.meanR)[2:ncol(traj.meanR)] <- unique(reduced_summary$baseSTAS)

fin.propR <- data.frame(Exploitation.Rate = unique(reduced_summary$baseER),  
                    matrix(reduced_summary$endsuc, 
                           nrow = length(unique(reduced_summary$baseER)), 
                           ncol = length(unique(reduced_summary$baseSTAS)), 
                           byrow = TRUE))

colnames(fin.propR)[2:ncol(fin.propR)] <- unique(reduced_summary$baseSTAS)

traj.propR <- data.frame(Exploitation.Rate = unique(reduced_summary$baseER),  
                    matrix(reduced_summary$trajprop, 
                           nrow = length(unique(reduced_summary$baseER)), 
                           ncol = length(unique(reduced_summary$baseSTAS)), 
                           byrow = TRUE))

colnames(traj.propR)[2:ncol(traj.propR)] <- unique(reduced_summary$baseSTAS)

```

### FS Categories
```{r}
full_summary %>% filter(baseSTAS <0.031) %>%
  mutate(endsucC = ifelse(endsuc < 0.11, "0-0.10", 
                          ifelse(endsuc >= 0.11 & endsuc <= 0.33, "0.11-0.33",
                                 ifelse(endsuc > 0.33 & endsuc < 0.66, "0.34-0.65",
                                        ifelse(endsuc >= 0.66 & endsuc < 0.9, "0.66-0.89", 
                                               "0.90-1"))))) %>%
ggplot(aes(x = baseSTAS, y = baseER, fill = endsucC, z = endsucC)) +
  geom_raster() +
  scale_y_reverse(expand = c(0, 0)) +
  scale_fill_manual(values = Ccols,
                       name = "Proportion of 'Final Success'") +
  theme(legend.position = "top", legend.text = element_text(size = 10),
        legend.title = element_text(size = 13)) +
  guides(fill = guide_legend(ncol = 2), title.position = "top") +
  labs(y = "Exploitation Rate", x = "Marine Survival") +
  #geom_contour() +
  scale_x_continuous(expand = c(0, 0)) +
  geom_segment(aes(x = minSTAS-0.0005, y = 0.15, xend = aveSTAS, yend = 0.15),
               colour = "blue", size = 1.2, alpha = 0.1) +
  geom_segment(aes(x = minSTAS-0.0005, y = 0.36, xend = aveSTAS, yend = 0.36),
               colour = "blue", size = 1.2, alpha = 0.1) +
  geom_segment(aes(x = minSTAS-0.0005, y = 0.2, xend = aveSTAS, yend = 0.2),
               colour = "blue", size = 1.2, alpha = 0.1) +
  geom_segment(aes(x = minSTAS-0.0005, y = 0.3, xend = aveSTAS, yend = 0.3),
               colour = "blue", size = 1.2, alpha = 0.1) +
  geom_segment(aes(x = minSTAS-0.0005, y = 0.45, xend = aveSTAS, yend = 0.45),
               colour = "blue", size = 1.2, alpha = 0.1) +
  geom_segment(aes(x = aveSTAS, y = 0.15, xend = aveSTAS, yend = maxER),
               colour = "blue", size = 1.2, alpha = 0.1) +
  annotate("text", x = aveSTAS + 0.001, y = 0.15, label = "3 Generation Mean", hjust = 0)+
  annotate("text", x = aveSTAS + 0.001, y = 0.35, label = "Umsy", hjust = 0)+
  annotate("text", x = aveSTAS + 0.001, y = 0.2, label = "PST Low", hjust = 0)+
  annotate("text", x = aveSTAS + 0.001, y = 0.3, label = "PST Moderate", hjust = 0)+
  annotate("text", x = aveSTAS + 0.001, y = 0.45, label = "PST Abundant", hjust = 0)
  # geom_segment(aes(x = minSTAS-0.0005, y = aveER+sdER, xend = STASsdlo, yend = aveER+sdER), 
  #              colour = "gray", linetype = 2, size = 1.2, alpha = 0.1) +
  # geom_segment(aes(x = minSTAS-0.0005, y = aveER-sdER, xend = STASsdhi, yend = aveER-sdER), 
  #              colour = "gray", linetype = 2, size = 1.2, alpha = 0.1) +
  # geom_segment(aes(x = STASsdlo, y = maxER, xend = STASsdlo, yend = aveER+sdER), 
  #              colour = "gray", linetype = 2, size = 1.2, alpha = 0.1) +
  # geom_segment(aes(x = STASsdhi, y = maxER, xend = STASsdhi, yend = aveER-sdER), 
  #              colour = "gray", linetype = 2, size = 1.2, alpha = 0.1)
  
ggsave(filename = paste("Data_out/", "Full_Sum_Final_Success_Cate_65",".png", sep = ""),
       width = 5, height = 5.75, units = "in", dpi = 500)
```

### PT Categories
```{r}
full_summary %>% filter(baseSTAS <0.031) %>%
  mutate(trajpropC = ifelse(trajprop < 0.11, "0-0.10", 
                          ifelse(trajprop >= 0.11 & trajprop <= 0.33, "0.11-0.33",
                                 ifelse(trajprop > 0.33 & trajprop < 0.66, "0.34-0.65",
                                        ifelse(trajprop >= 0.66 & trajprop < 0.9, "0.66-0.89", 
                                               "0.90-1"))))) %>%
ggplot(aes(x = baseSTAS, y = baseER, fill = trajpropC, z = trajpropC)) +
  geom_raster() +
  
  scale_y_reverse(expand = c(0, 0)) +
  scale_fill_manual(values = Ccols,
                       name = "Proportion of 'Positive Trajectories'") +
  theme(legend.position = "top", legend.text = element_text(size = 10),
        legend.title = element_text(size = 13)) +
  guides(fill = guide_legend(ncol = 2), title.position = "top") +
  labs(y = "Exploitation Rate", x = "Marine Survival") +
  #geom_contour() +
  scale_x_continuous(expand = c(0, 0)) +
  geom_segment(aes(x = minSTAS-0.0005, y = 0.15, xend = aveSTAS, yend = 0.15),
               colour = "blue", size = 1.2, alpha = 0.1) +
  geom_segment(aes(x = minSTAS-0.0005, y = 0.36, xend = aveSTAS, yend = 0.36),
               colour = "blue", size = 1.2, alpha = 0.1) +
  geom_segment(aes(x = minSTAS-0.0005, y = 0.2, xend = aveSTAS, yend = 0.2),
               colour = "blue", size = 1.2, alpha = 0.1) +
  geom_segment(aes(x = minSTAS-0.0005, y = 0.3, xend = aveSTAS, yend = 0.3),
               colour = "blue", size = 1.2, alpha = 0.1) +
  geom_segment(aes(x = minSTAS-0.0005, y = 0.45, xend = aveSTAS, yend = 0.45),
               colour = "blue", size = 1.2, alpha = 0.1) +
  geom_segment(aes(x = aveSTAS, y = 0.15, xend = aveSTAS, yend = maxER),
               colour = "blue", size = 1.2, alpha = 0.1) +
  annotate("text", x = aveSTAS + 0.001, y = 0.15, label = "3 Generation Mean", hjust = 0)+
  annotate("text", x = aveSTAS + 0.001, y = 0.35, label = "Umsy", hjust = 0)+
  annotate("text", x = aveSTAS + 0.001, y = 0.2, label = "PST Low", hjust = 0)+
  annotate("text", x = aveSTAS + 0.001, y = 0.3, label = "PST Moderate", hjust = 0)+
  annotate("text", x = aveSTAS + 0.001, y = 0.45, label = "PST Abundant", hjust = 0) #+
  
  #geom_segment(aes(x = minSTAS-0.0005, y = aveER+sdER, xend = STASsdlo, yend = aveER+sdER), 
               #colour = "gray", linetype = 2, size = 1.2, alpha = 0.1) +
  #geom_segment(aes(x = minSTAS-0.0005, y = aveER-sdER, xend = STASsdhi, yend = aveER-sdER), 
               #colour = "gray", linetype = 2, size = 1.2, alpha = 0.1) +
  #geom_segment(aes(x = STASsdlo, y = maxER, xend = STASsdlo, yend = aveER+sdER), 
               #colour = "gray", linetype = 2, size = 1.2, alpha = 0.1) +
  #geom_segment(aes(x = STASsdhi, y = maxER, xend = STASsdhi, yend = aveER-sdER), 
               #colour = "gray", linetype = 2, size = 1.2, alpha = 0.1)


ggsave(filename = paste("Data_out/", "Full_Sum_Positive_Traj_Cate",".png", sep = ""),
       width = 5, height = 5.75, units = "in", dpi = 500)
```

